### 2018-03-16 paper.Rmd
refs

```{r load_packages, echo = FALSE}
library(papaja)
library(tidyverse)
library(childesr)
library(directlabels)
knitr::opts_chunk$set(cache = TRUE, echo = FALSE)
```

@@

Since its inception, a tremendous corpus of research has made use of CHILDES data. Individual studies are too numerous to list, but  classics include studies of morphological over-regularization [@marcus1992], distributional learning [@redington1998], word segmentation [@goldwater2009], the role of frequency in word learning [@goodman2008] and many others. Some studies analyze individual examples in depth [e.g., @snider2007] while others work with the corpus as a whole [e.g., @meylan2017]. These are just a few of the thousands of studies that take CHILDES corpora -- transcripts, annotations, and associated media -- as starting points.

@@

This practice is problematic for a number of reasons. Effort wasted in rewriting the same parser again and again. In addition, this process introduces a major source of errors and inconsistencies in data handling due to difficulties dealing with the many special cases in the CHAT standard. Further, these scripta are rarely shared, leading to much greater difficulty in reproducing the exact numerical results from papers using CHILDES [see e.g., @meylan2017]. This lack of computational reproducibility is widely recognized as problematic because it does not allow researchers to verify or build on published researcher [@donohoe2010,@stodden2016]. Finally, the CHILDES corpus itself is a moving target;  computational work using the entire corpus at one time point may include a different set of data than subsequent work (due to new contributions or revisions).

@@

>>>>

```{r load_packages, echo = FALSE, warning=FALSE}
library(papaja)
library(tidyverse)
library(childesr)
library(directlabels)
knitr::opts_chunk$set(cache = TRUE, echo = FALSE)
```

@@

Since its inception, a tremendous corpus of research has made use of CHILDES data. Individual studies are too numerous to list, but  classics include studies of morphological over-regularization [@marcus1992], distributional learning [@redington1998], word segmentation [@goldwater2009], the role of frequency in word learning [@goodman2008] and many others. Some studies analyze individual examples in depth [e.g., @snyder2007] while others work with the corpus as a whole [e.g., @meylan2017]. These are just a few of the thousands of studies that take CHILDES corpora -- transcripts, annotations, and associated media -- as starting points.

@@

This practice is problematic for a number of reasons. Effort wasted in rewriting the same parser again and again. In addition, this process introduces a major source of errors and inconsistencies in data handling due to difficulties dealing with the many special cases in the CHAT standard. Further, these scripta are rarely shared, leading to much greater difficulty in reproducing the exact numerical results from papers using CHILDES [see e.g., @meylan2017]. This lack of computational reproducibility is widely recognized as problematic because it does not allow researchers to verify or build on published researcher [@donoho2010,@stodden2016]. Finally, the CHILDES corpus itself is a moving target;  computational work using the entire corpus at one time point may include a different set of data than subsequent work (due to new contributions or revisions).

@@

# Acknowledgements
- Brian MacWhinney for CHILDES
- Melissa Kline for ClanToR
